\chapter{Conclusion and Recommendations}

\section{Recommendations}
I recommend to allow students engage in internship trainings at every end of the study year this will help students gain more experience, skills and knowledge. Students will also get used to the real working world hence producing competent graduates with enough experience and skills. \\ \\
I also recommend the university to improve on the teaching mode by engaging students more in practical projects rather than waiting for the final year project.

\section{Conclusion}
In conclusion, this training period has been so nice that have been able to practically apply my theory, acquire more knowledge by cooperating with my field supervisor through asking what I don’t know and learn very many things.  \\ \\
And I think this training was worthy it to be done. Thank all staff of Banana Phone World Ltd so much for their support, encouragement, conducive working environment and training because have I gained a lot. \\ \\
I thank the University for such an Arrangement because it’s very useful and also helps to produce practical oriented graduates. The idea of industrial training is very good since students are able to learn a lot of practical work, get exposed to the outside world and potential employers, this helps them after their course to get to appreciate their profession hence get better ethics and an opportunity to put to use their theoretically acquired knowledge into practical things. It was also a great experience being at the training where all that I had seen in books were laid bare and done by me.
